---
title: "The Beta-Binomial Model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{beta-binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bayesrules)
```

The **bayesrules** package has five functions to support learning about the beta-binomial model. The two of the functions, `plot_beta()` and `summarize_beta()` are intended to be used for understanding the prior (or the posterior) Beta distribution.

## Prior

```{r fig.align='center'}
plot_beta(alpha = 3, beta = 13, mean = TRUE, mode = TRUE)
```

```{r}
summarize_beta(alpha = 3, beta = 13)
```


## Likelihood

In addition `plot_binomial_likelihood()` helps users visualize the likelihood function and shows the maximum likelihood estimation.

```{r fig.align='center', fig.height=4, fig.width=5, message = FALSE}
plot_binomial_likelihood(x = 3, n = 15, mle = TRUE)
```


This function is solely built for educational purposes and the default setting for values $\pi$ is `seq(0, 1, by = 0.01)`. However users can specify the support with the `pi` argument. One can make pi purely discrete by setting pi to specific values such as `pi = c(0, 0.25, 0.4, 0.92)` or trick to function to make the support of pi more like continuous.

```{r fig.align='center', fig.height=4, fig.width=5, message = FALSE}
plot_binomial_likelihood(x = 3, n = 15, mle = TRUE, seq(0, 1, by = 0.002))
```


## Prior-Likelihood-Posterior

The two other functions `plot_beta_binomial()` and `summarize_beta_binomial()` require both the prior parameters and the data for the likelihood. 

```{r fig.align='center', warning = FALSE, fig.height=4, fig.width=5}
plot_beta_binomial(alpha = 3, beta = 13, x = 5, n = 10, 
                   prior = TRUE, #the default 
                   likelihood = TRUE,  #the default
                   posterior = TRUE #the default
                   )
```

