---
title: "The Beta-Binomial Model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bayesian-models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bayesrules)
```

The **bayesrules** package has four functions to support learning about the beta-binomial model. The two of the functions, `plot_beta()` and `summarize_beta()` are intended to be used for understanding the prior (or the posterior) Beta distribution.

```{r fig.align='center'}
plot_beta(alpha = 3, beta = 13, mean = TRUE, mode = TRUE)
```

```{r}
summarize_beta(alpha = 3, beta = 13)
```

The two other functions `plot_beta_binomial()` and `summarize_beta_binomial()` require both the prior parameters and the data for the likelihood. 

```{r fig.align='center', warning = FALSE, fig.height=6, fig.width=5}
plot_beta_binomial(alpha = 3, beta = 13, x = 5, n = 10, 
                   prior = TRUE, #the default 
                   likelihood = TRUE,  #the default
                   posterior = TRUE #the default
                   )
```

